---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

Unzip and load the csv file

``` {r simulation, echo = TRUE}
unzip(zipfile="activity.zip")
act_data <- read.csv("activity.csv")
```


## What is mean total number of steps taken per day?
Load needed libraries
``` {r}
library(ggplot2)
```
Make a histogram of the total number of steps taken each day
``` {r}
totnum.steps <- tapply(act_data$steps, act_data$date, FUN=sum, na.rm=TRUE)
# qplot(totnum.steps, binwidth=1000, xlab="Total number of steps taken each day")
hist(totnum.steps,main='Total number of steps per day',xlab='Total number of steps per day',col='blue')
```

Calculate and report the mean and median of the total number of steps taken per day
``` {r}
mean(totnum.steps, na.rm=TRUE)
median(totnum.steps, na.rm=TRUE)
```


## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
